Modularly Metaprogrammable Type Structure (Supplemental Material)

### 2015-05-28 atlam-icfp15/att-pldi15-supplement.tex
ICFP 15

\title{Modularly Composing Typed Language Fragments (Supplemental Material)}
%\subtitle{Supplemental Material}
%\authorinfo{}{}{}
%\authorinfo{Cyrus Omar \and Jonathan Aldrich}
 %         {Carnegie Mellon University}
  %         {\{comar, aldrich\}@cs.cmu.edu}

@@

\abstract{
    This document provides the full technical development described in the paper ``Modularly Composing Typed Language Fragments'' submitted to PLDI 2015. 
}
\keywords{Statistical Model Checking, Markov Decision Processes, Reinforcement Learning}

@@

\subsection{Internal Statics}
We assume an internal language where the statics are specified in the standard way by judgements for  type formation {$\iDelta \vdash \tau$}, shown in Figure \ref{fig:internal-type-formation}, typing context formation { $\iDelta \vdash \iGamma$}, shown in Figure \ref{fig:internal-typing-context-formation}, and type assignment {$\iDelta~\iGamma \vdash \iota : \tau\moutput$}, shown in Figure \ref{fig:internal-type-asignment}. \todo{do these and cite relevant rules in remainder}
%The typing and type formation contexts obey standard structural properties (i.e. weakening, exchange and contraction).

@@

\subsection{Conservativity}
\subsubsection{Backprojection}
To avoid having to give a large number of rules that do nothing interesting, we define backprojection on static terms definitionally.\todo{eval of index should be empty Phi}

@@

This section has, obviously, been less detailed than the remainder of the supplement, essentially because the lemmas above involve a rather large number of cases where nothing of note is happening, and we simply ran out of time to inductively specify the full details of backprojection and prove all of them. Backprojection is a rather simple conceptual mapping, so we believe that the level of detail above is sufficiently convincing, and we plan on writing out the full details (which we anticipate will be another 20 or so pages) well before the notification date.

% \subsection{Decidability}
% Not going to prove this so probably take it out.
\section{Discussion}
\subsection{Record Types}
In the paper, we presented labeled products rather than the more conventional record types, both to emphasize that different variants have different trade-offs, and because it made our examples simpler.

One strategy for supporting records themselves would be to specify the intro operator such that records that do not have sorted indices are uninhabited, then provide a helper static function that generates only sorted indices and require that all type construction pass through that. This notion of a ``type constructor constructor'' could perhaps be integrated into the calculus.

An alternative strategy may have been to use an abstract kind that ensured that such type indices could not have been constructed, but to be compatible with our equality kind restriction, this would require support for abstract equality kinds, analagous to abstract equality types in SML. We chose not to formalize these for simplicity, and to demonstrate the general technique above. This could also have been used for the labeled product example.

>>>>

\title{Modularly Metaprogrammable Type Structure (Supplemental Material)}
%\subtitle{Supplemental Material}
%\authorinfo{}{}{}
%\authorinfo{Cyrus Omar \and Jonathan Aldrich}
 %         {Carnegie Mellon University}
  %         {\{comar, aldrich\}@cs.cmu.edu}

@@

\abstract{
    This document provides more complete technical development described in the paper ``Modularly Metaprogrammable Type Structure'' submitted to ICFP 2015. 
}
\keywords{Statistical Model Checking, Markov Decision Processes, Reinforcement Learning}

@@

\subsection{Internal Statics}
We assume an internal language where the statics are specified in the standard way by judgements for  type formation {$\iDelta \vdash \tau$}  typing context formation { $\iDelta \vdash \iGamma$}, and type assignment {$\iDelta~\iGamma \vdash \iota : \tau\moutput$}.
%The typing and type formation contexts obey standard structural properties (i.e. weakening, exchange and contraction).

@@

\subsection{Conservativity}
\subsubsection{Backprojection}
To avoid having to give a large number of rules that do nothing interesting, we define backprojection on static terms definitionally.%\todo{eval of index should be empty Phi}

@@

This section needs a bit more detail, essentially because the lemmas above involve a rather large number of cases where nothing of note is happening, and we simply ran out of time to inductively specify the full details of backprojection and prove all of them. Backprojection is a rather simple conceptual mapping, so we believe that the level of detail above is sufficiently convincing, and we plan on writing out the full details (which we anticipate will be another 20 or so pages) well before the notification date.

% \subsection{Decidability}
% Not going to prove this so probably take it out.
\section{Discussion}
% \subsection{Record Types}
% In the paper, we presented labeled products rather than the more conventional record types, both to emphasize that different variants have different trade-offs, and because it made our examples simpler.

% One strategy for supporting records themselves would be to specify the intro operator such that records that do not have sorted indices are uninhabited, then provide a helper static function that generates only sorted indices and require that all type construction pass through that. This notion of a ``type constructor constructor'' could perhaps be integrated into the calculus.

% An alternative strategy may have been to use an abstract kind that ensured that such type indices could not have been constructed, but to be compatible with our equality kind restriction, this would require support for abstract equality kinds, analagous to abstract equality types in SML. We chose not to formalize these for simplicity, and to demonstrate the general technique above. This could also have been used for the labeled product example.
